### 2019-08-06 1_introduction.tex
Small wording tweak from Alex.
Tweak some wording around GPU text.

Note that a lower METG does not necessarily mean that 
performance for a particular workload is better. For example, two systems with METG(50\%) of 100~\textmu{}s and 1~ms,
respectively, running an application with an average task granularity
of 10~ms, are both very likely to perform well. Only when the task
granularity approaches (or drops below) METG(50\%) will performance
likely diverge. Thus METG helps to identify the regime in which a
given system can deliver good performance, and explains how
different systems coexist with runtime overheads that vary by orders of magnitude.

@@

The paper is organized as follows: Section~\ref{sec:task-bench}
describes the design of Task Bench, Section~\ref{sec:implementation}
discusses the implementation of Task Bench in 15 programming systems,
Section~\ref{sec:metg} defines the METG metric and its
relationship to quantities of interest to application developers,
Section~\ref{sec:evaluation} provides a comprehensive evaluation of
Task Bench on up to 256 Haswell nodes of the Cori
supercomputer~\cite{Cori}, Section~\ref{sec:related-work} relates this
work to previous efforts, and Section~\ref{sec:conclusion} concludes.

>>>>

A lower METG does not necessarily mean that
performance for a particular workload is better. For example, two systems with METG(50\%) of 100~\textmu{}s and 1~ms,
respectively, running an application with an average task granularity
of 10~ms, are both very likely to perform well. Only when the task
granularity approaches (or drops below) METG(50\%) will performance
likely diverge. Thus METG helps to identify the regime in which a
given system can deliver good performance, and explains how
different systems coexist with runtime overheads that vary by orders of magnitude.

@@

The paper is organized as follows: Section~\ref{sec:task-bench}
describes the design of Task Bench. Section~\ref{sec:implementation}
discusses implementations in 15 programming systems.
Section~\ref{sec:metg} defines the METG metric and its
relationship to quantities of interest to application developers.
Section~\ref{sec:evaluation} provides a comprehensive evaluation of
Task Bench on up to 256 Haswell nodes of the Cori
supercomputer~\cite{Cori} (GPU results are reported on Piz Daint~\cite{PizDaint}). Section~\ref{sec:related-work} relates to previous efforts; Section~\ref{sec:conclusion} concludes.

### 2019-08-06 5_evaluation.tex
Tweak some wording around GPU text.

Figure~\ref{fig:cuda-efficiency} compares MPI
and MPI+CUDA on the Piz Daint supercomputer. The CUDA
compute kernel achieves a peak performance of $4.759 \times 10^{12}$
FLOP/s, which is very close to the officially reported number
$4.761 \times 10^{12}$. The CPU achieves $5.726 \times 10^{11}$
FLOP/s. Note that the kernels perform different numbers of
operations as the GPU requires more work to reach peak
performance. The x-axis in Figure~\ref{fig:cuda-efficiency} has been
normalized to keep FLOPs constant for a given problem
size.

>>>>

In order to determine the cost of scheduling tasks on the GPU, Figure~\ref{fig:cuda-efficiency} compares MPI
and MPI+CUDA on the Piz Daint supercomputer. The CUDA
compute kernel achieves a peak performance of $4.759 \times 10^{12}$
FLOP/s, which is very close to the officially reported number
$4.761 \times 10^{12}$. The CPU achieves $5.726 \times 10^{11}$
FLOP/s. Note that the kernels perform different numbers of
operations as the GPU requires more work to reach peak
performance. The x-axis in Figure~\ref{fig:cuda-efficiency} is
normalized to keep FLOPs constant for a given problem
size.
